Quantifying the home advantage with `hyper3` objects

### 2023-01-27 inst/home_advantage3.Rmd
further likelihood analysis

We can proceed in two ways.  The flaw in this analysis is that it is
conditional on the estimated value of $\lambda$ [which is not too bad,
IMO].  Secondly

>>>>

Or even

```{r,label=optimlam,cache=TRUE}
op <- optimize(f,interval=c(2,3),maximum=TRUE)
op
```

We can proceed in two ways.  Firstly we can use $\hat{\lambda}$ directly:

```{r,ept,cache=TRUE}
equalp.test(home_away3(M,lambda=op$maximum))
```

The flaw in this analysis is that it is conditional on the estimated
value of $\lambda$ [which is not too bad, IMO].  Secondly we can
perform a fully 2D analysis, which allows for the fact that the
evaluate might have a different value of $\lambda$ from the
$\hat{\lambda}$:
